Results visualization across sites

### 2021-11-09 metanalysis_visualization/visualization.Rmd
new markdown for the visualization added

---
title: "pediatricResults"
author: "aGutierrezSacristan"
date: "10/26/2021"
output: html_document
---
```{r libraries, message=FALSE, warning=FALSE, results='hide'}
# Install packages
paket <- function(pak){
  new_pak <- pak[!(pak %in% rownames(installed.packages()))]
  if (length(new_pak)) 
    install.packages(new_pak, dependencies = TRUE,repos="https://cloud.r-project.org/")
  sapply(pak, library, character.only = TRUE)
}
listOfPackages <- c("tidyverse", "RColorBrewer", "knitr", "kableExtra", "tsModel", "gridExtra", "dplyr", "metafor", "meta", "viridis")
paket(listOfPackages)
```

@@

```{r}
outputDir <- "../output/"
outputFiles <- list.files( path = outputDir, pattern = "\\.RData")
getwd()
```

@@

## Patient Count with Mental Health Related ICD codes

```{r}
thpd_psyCount <- count_icd_all %>%
  pivot_longer(names_to = "counts", cols=c(count_psy, count_icd)) %>%
  mutate( counts = ifelse( counts == "count_psy", "Psy", "Total")) %>%
  ggplot(aes(x = time_p, y = value, fill = counts, color = counts)) +
  facet_grid(siteid~.) +
  geom_point() +
  geom_vline(xintercept = as.Date(pandemic_start_date),
             linetype = "dashed") +
  scale_fill_manual(values = cbPalette) +
  scale_color_manual(values = cbPalette) +
  labs(y = "Counts",
       x = paste0("Date (by ", time_period,")"),
       title = paste0("Per ", time_period , " patient counts with mental health related ICD codes")) + 
  geom_smooth(method = "lm", formula = y ~ splines::ns(x, 2), se = TRUE, aes(colour=period), colour= "black", size = 0.5)
thpd_psyCount
```

#### Both results together

```{r}
count_icd_all_combined <-  count_icd_all %>%
  group_by(time_p, period) %>% 
  summarise(count_psy_all = sum(count_psy), 
            count_icd_all = sum( count_icd ))

thpd_psyCount_combined <- count_icd_all_combined %>%
  pivot_longer(names_to = "counts", cols=c(count_psy_all, count_icd_all)) %>%
  mutate( counts = ifelse( counts == "count_psy_all", "Psy", "Total")) %>%
  ggplot(aes(x = time_p, y = value, fill = counts, color = counts)) +
  geom_point() +
  geom_vline(xintercept = as.Date(pandemic_start_date),
             linetype = "dashed") +
  scale_fill_manual(values = cbPalette) +
  scale_color_manual(values = cbPalette) +
  labs(y = "Counts",
       x = paste0("Date (by ", time_period,")"),
       title = paste0("Per ", time_period , " patient counts with mental health related ICD codes")) + 
  geom_smooth(method = "lm", formula = y ~ splines::ns(x, 2), se = TRUE, aes(colour=period), colour= "black", size = 0.5)
thpd_psyCount_combined
```

## Ratio patients with vs without psychiatric conditions
```{r}
ratio_psy_non_psy <- ratios_patients_with_without_psy_all %>%
  ggplot(aes(x = time_p, y = ratio, fill = period, color = period)) +
  geom_point() +
  facet_grid(siteid~.) +
  geom_vline(xintercept = as.Date(pandemic_start_date),
             linetype = "dashed") +
  scale_fill_manual(values = cbPalette) +
  scale_color_manual(values = cbPalette) +
  labs(y = "Ratio (with psy conditions/without psy conditions)",
       x = paste0("Date (by ", time_period,")"),
       title = paste0("Ratio patient with vs without psychiatric conditions ( per ", time_period,")"))

ratio_psy_non_psy
```

## Percenge patients with vs without psychiatric conditions
```{r}
percentage_psy_non_psy <- ratios_patients_with_without_psy_all %>%
  ggplot(aes(x = time_p, y = percentage, color = period)) +
  facet_grid(siteid~.) +
  geom_point() +
  geom_vline(xintercept = as.Date(pandemic_start_date),
             linetype = "dashed") +
  scale_fill_manual(values = cbPalette) +
  scale_color_manual(values = cbPalette) +
  labs(y = "Percentage",
       x = paste0("Date (by ", time_period,")"),
       title = paste0("Percentage patient with vs total population ( per ", time_period,")")) +
  guides(color = guide_legend(title="Patient diagnoses types"))

percentage_psy_non_psy
```

### Test meta-analysis percentage

```{r}
#split this into before and after pandemic and run it twice (one for each subset)

@@

#### Overlap lines: one per site
```{r}
ratios_patients_with_without_psy_all %>%
  ggplot( aes(x=as.factor(time_p), y=ratio, 
              group = siteid, color = siteid))+
  geom_point() + 
  geom_line() +
  scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    theme(
      legend.position="bottom",
      plot.title = element_text(size=11)
    ) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 6)) +
    ggtitle("Dot and line plot") +
    xlab("period (months)")

#### Meta-analysis of temporal trends

>>>>

---
title: "Results visualization across sites"
output:
  html_document:
    code_folding: hide
    toc: yes
    toc_float: yes
editor_options: 
  markdown: 
    wrap: 72
---

## Setting up the R environment

### Installing packages and loading the library

```{r libraries, message=FALSE, warning=FALSE, results='hide'}
# Install packages
paket <- function(pak){
  new_pak <- pak[!(pak %in% rownames(installed.packages()))]
  if (length(new_pak)) 
    install.packages(new_pak, dependencies = TRUE,repos="https://cloud.r-project.org/")
  sapply(pak, library, character.only = TRUE)
}
listOfPackages <- c("tidyverse", "RColorBrewer", "knitr", "kableExtra", "tsModel", "gridExtra", "dplyr", "metafor", "meta", "viridis")
paket(listOfPackages)
```

### R session information

```{r, results='hide'}
sessionInfo()
```

@@

```{r}
outputDir <- "../../output/"
outputFiles <- list.files( path = outputDir, pattern = "\\.RData")
country_map <- read.delim( file = paste0( outputDir, "country_mapping.txt"))
getwd()
```

@@

## Percentage: patients with psychiatric conditions / total number of patients

### By site

```{r}
ratios_patients_with_without_psy_all %>%
  filter(time_p <= history_end_date &
         time_p >= history_start_date ) %>%
  ggplot( aes(x=time_p, y=percentage, 
              group = siteid, color = siteid))+
  geom_point( aes(shape=siteid, color=siteid) )+
    geom_line() +
  geom_vline(xintercept = as.Date(pandemic_start_date),
             linetype = "dashed") +
  scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    theme(
      legend.position="bottom",
      plot.title = element_text(size=11)
    ) +
  scale_x_date(date_labels = "%b-%d-%Y", breaks = "month") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 6)) +
    ggtitle("Percentage: patients with psychiatric conditions / total number of patients") +
    xlab("period (months)")
```

### By Country

```{r}
ratios_patients_with_without_psy_all_country <- left_join( ratios_patients_with_without_psy_all, country_map )
ratios_patients_with_without_psy_all_country %>%
    filter(time_p <= history_end_date &
         time_p >= history_start_date )  %>%
  ggplot(aes(x = time_p, y = percentage, fill = siteid, color = siteid)) +
  geom_point( aes(shape=siteid, color=siteid)  ) +
  geom_line() +
  facet_grid(country~.) +
  geom_vline(xintercept = as.Date(pandemic_start_date),
             linetype = "dashed") +
  scale_fill_manual(values = cbPalette) +
  scale_color_manual(values = cbPalette) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 6)) +
  scale_x_date(date_labels = "%b-%d-%Y", breaks = "month", limits = c( history_start_date, history_end_date  )) +
  labs(y = "Ratio (with psy conditions/without psy conditions)",
       x = paste0("Date (by ", time_period,")"),
       title = paste0("Percentage: patients with psychiatric conditions / total number of patients ( per ", time_period,")"))
```

## Ratio: patients with vs. patients without psychiatric conditions

### By site
```{r}
ratios_patients_with_without_psy_all %>%
  filter(time_p <= history_end_date &
         time_p >= history_start_date ) %>%
  ggplot( aes(x=time_p, y=ratio, 
              group = siteid, color = siteid))+
  geom_point( aes(shape=siteid, color=siteid) ) + 
  geom_line() +
  geom_vline(xintercept = as.Date(pandemic_start_date),
             linetype = "dashed") +
  scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    theme(
      legend.position="bottom",
      plot.title = element_text(size=11)
    ) +
  scale_x_date(date_labels = "%b-%d-%Y", breaks = "month") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 6)) +
    ggtitle("Ratio: patients with vs. patients without psychiatric conditions") +
    xlab("period (months)")

### By Country

```{r}
ratios_patients_with_without_psy_all_country %>%
    filter(time_p <= history_end_date &
         time_p >= history_start_date ) %>%
  ggplot(aes(x = time_p, y = ratio, fill = siteid, color = siteid)) +
  geom_point( aes(shape=siteid, color=siteid)  ) +
  geom_line() +
  facet_grid(country~.) +
  geom_vline(xintercept = as.Date(pandemic_start_date),
             linetype = "dashed") +
  scale_fill_manual(values = cbPalette) +
  scale_color_manual(values = cbPalette) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 6)) +
  scale_x_date(date_labels = "%b-%d-%Y", breaks = "month", limits = c( history_start_date, history_end_date  )) +
  labs(y = "Ratio (with psy conditions/without psy conditions)",
       x = paste0("Date (by ", time_period,")"),
       title = paste0("Ratio patient with vs without psychiatric conditions ( per ", time_period,")"))
```

## Meta-analysis percentage

```{r, results='hide', fig.show='hide'}
#split this into before and after pandemic and run it twice (one for each subset)

@@

## Meta-analysis of temporal trends
